MLISA: Machine Learning-based \\ Intelligent Service Agents

### 2014-11-25 papers/webservice-coalition-learning/webservice_coalition_learning.tex
changes

text text

>>>>

In this paper, we proposed a training model for the problem of membership management of communities of web services. Using the traning model we created a decision making profile for each community and web service involved which provides them with a set of feasible and utility increasing moves. This utilized our web services with efficient methods of foreseeing how their choices of actions would impact their long-term and short-term goals, therefore they opted for best decision available. The ultimate goal is to choose the best decision when it comes to communities formation, among many possible short-term rational and utility increasing choices. The experimental results show that our algorithms provide web services and community owners, in real-world-like environments, with applicable and near-perfect decision making mechanisms.

Our plan for future work is to advance learning process on the training set that we provided in our work. SVN machine learning algorithm are suitable in classification of our training data set, to better classify correct or wrong decisions based on long-term utility gains, as data set outputs. This can further facilitate the process of finding optimal cooperators in regards to enhancing web services' overall performance as service providers.
